### 2019-05-24 scache/jpdc/tex/impl.tex
mkdir scache

To prove the cross-framework capability of SCache, we adapt SCache on Hadoop MapReduce and Spark respectively. In Hadoop MapReduce, we modify codes in ResourceManager, MapTask, and ReduceTask to call SCache APIs through RPC. It takes about 380 lines of code. In Spark, we mainly modify DAGScheduler and the corresponding data fetcher. 
It only takes about 500 lines of code. Such hundreds of lines of code modification are very small compared to the hundreds of thousands of lines of code in DAG framework. We believe that the costs of enabling SCache on other DAG computing frameworks, such as Tez \cite{tez}, are also very low.
}

\subsection{Fault tolerance}\label{fault}
Due to the characteristic of shuffle data (e.g., short-lived, write-once, read-once), we believe fault tolerance is not a crucial goal of SCache at present. 
We plan to implement SCache master with Apache ZooKeeper \cite{zookeeper} to provide constantly service. 
If a failure happened inside the SCache worker, SCache daemon could block the shuffle write/read operations until the worker process restarted without violating the correctness of the DAG computing.
A possible way to handle this failure is selecting some backup nodes to store replications. 
But the replications can introduce a significant network overhead \cite{availability}.  
Currently, we left the sever faults (e.g., the failure of a node) to the DAG frameworks. 
We believe it is a more promising way because most DAG frameworks have more advanced fast recovery schemes on the application layer, such as paralleled recovery of Spark. 
Meanwhile, SCache can still provide shuffle optimization during the recovery.

>>>>

To prove the cross-framework capability of SCache, we adapt SCache on Hadoop MapReduce and Spark respectively. In Hadoop MapReduce, we modify codes in ResourceManager, MapTask, and ReduceTask to call SCache APIs through RPC. It takes about 380 lines of code. In Spark, we mainly modify DAGScheduler and the corresponding data fetcher. 
It only takes about 500 lines of code. Such hundreds of lines of code modification are very small compared to the hundreds of thousands of lines of code in DAG framework. We believe that the costs of enabling SCache on other DAG computing frameworks, such as Tez \cite{tez}, are also low.
}

\subsection{Fault tolerance}\label{fault}
Due to the characteristic of shuffle data (e.g., short-lived, write-once, read-once), we believe fault tolerance is not a crucial goal of SCache at present. 
We plan to implement SCache master with Apache ZooKeeper \cite{zookeeper} to provide constantly service. 
If a failure happens inside the SCache worker, SCache daemon can block the shuffle write/read operations until the worker process restarts without violating the correctness of the DAG computing.
A possible way to handle this failure is selecting some backup nodes to store replications. 
But the replications can introduce a significant network overhead \cite{availability}.  
Currently, we leave the sever faults (e.g., the failure of a node) to the DAG frameworks. 
We believe it is a more promising way because most DAG frameworks have more advanced fast recovery schemes on the application layer, such as paralleled recovery of Spark. 
Meanwhile, SCache can still provide shuffle optimization during the recovery.

### 2019-05-24 scache/taco/tex/optimization.tex
mkdir scache

For the most DAG applications with random large scale input, 
the $BlockSize_{ji}$ in a particular shuffle can be predicted accurately by liner regression model (i.e., equation \ref{linearregresion}) based on observation that the ratio of map output size and input size are invariant given the same job configuration \cite{guo2017ishuffle, predict}: 
\begin{equation}
\label{linearregresion}
\begin{aligned}
	BlockSize_{ji} = a \times inputSize_j + b
\end{aligned}
\end{equation}
The $inputSize_j$ is the input size of $j$th map task. 
The $a$ and $b$ can be determined using the observed $inputSize_j$ and $BlockSize_{ji}$.

\begin{figure*}
	\centering
	\begin{subfigure}[b]{0.31\linewidth}
		\includegraphics[width=\linewidth]{fig/hash_pre}
		\caption{Linear Regression Prediction of Hash Partitioner\newline}
		\label{fig:hash_pre}
	\end{subfigure}
	\begin{subfigure}[b]{0.31\linewidth}
		\includegraphics[width=\linewidth]{fig/range_pre_sample}
		\caption{Linear Regression and Sampling Prediction of Range Partitioner2222}
		\label{fig:range_pre_sample}
		\vspace{1em}
	\end{subfigure}
	\begin{subfigure}[b]{0.31\linewidth}
		\includegraphics[width=\linewidth]{fig/prediction_relative_error}
		\caption{Prediction Relative Error of Range Partitioner\newline}
		\label{fig:prediction_relative_error}
	\end{subfigure}
	\caption{Reduction Distribution Prediction}
	\label{fig:dis}
	\vspace{-1em}
\end{figure*}

@@

\noindent
\begin{minipage}{0.95\columnwidth}
\begin{algorithm}[H]
\caption{Heuristic MinHeap Scheduling for Single Shuffle}
\label{hminheap}
	\begin{algorithmic}[1]
	\small
	\Procedure{schedule}{$m, host\_ids, p\_reduces$}
		\State $m\gets$ partition number of map tasks
		\State $R\gets$ sort $p\_reduces$ by size in non-increasing order
		\State $M\gets$ min-heap $\left\{ host\_id \rightarrow \left( \left[ reduces \right], size \right) \right\}$
		\State $idx\gets 0$
		\While{$idx <$ len$R$}
		% \Comment{Schedule reduces by MinHeap}
		\State $M\left[0\right].size \mathrel{+}= R\left[idx\right].size$
		\State $M\left[0\right].reduces.append\left(R\left[idx\right]\right)$
		\State $R\left[idx\right].assigned\_id \gets M \left[0\right].host\_id$
		\State Sift down $M\left[0\right]$ by $size$
		\State $idx\gets idx-1$
		\EndWhile
		\State $max\gets$ maximum size in $M$
		% \State Convert $M$ to mapping $\left\{ host\_id \rightarrow \left( \left[ rid\_arr \right], size \right) \right\}$
		\ForAll{$reduce$ in $R$}
		\Comment{Heuristic locality swap}
			\If{$reduce.assigned\_id \neq reduce.host\_id$}
				\State $p\gets reduce.prob$
				\State $norm\gets \left(p-1/m\right)/\left(1-1/m\right)/10$
				\State $upper\_bound \gets \left(1 + norm\right) \times max$
				\State SWAP\_TASKS$\left(M, reduce, upper\_bound\right)$
			\EndIf
		\EndFor
		\Return $M$
	\EndProcedure
	\Procedure{swap\_tasks}{$M, reduce, upper\_bound$}
		\State Swap tasks between node $host\_id$ and node $assigned\_id$
		\State of $reduce$ without exceeding the $upper\_bound$
		\State of both nodes.
		\State Return if it is impossible.
	\EndProcedure
	\end{algorithmic}
\end{algorithm}
\end{minipage}

To handle this corner case, we introduce another methodology, named \emph{weighted reservoir sampling}, as a substitution of linear regression. 
Note that linear regression will be replaced only when a RangePartitioner or a customized non-hash partitioner occurs. 
For each map task, we use classic reservoir sampling to randomly pick $s \times p$ of samples, where $p$ is the number of reduce tasks and $s$ is a tunable number. 
After that, the map function is called locally to process the sampled data (\textit{Sampling} in Figure \ref{fig:shuffle}). 
Finally, the partitioned outputs are collected with the $InputSize_j$ as the weight of the samples.
Note that sampling does not consume the input data of map tasks. 
The $BlockSize_{ji}$ can be calculated by:
\begin{equation}
\label{equationsample}
\begin{aligned}
	BlockSize_{ji} &= {{InputSize_j \times \frac{sample_i}{s \times p}}} \\
	sample_i &= \text{number of samples for $reduce_i$}
\end{aligned}
\end{equation}
% The classic reservoir sampling is designed for randomly choosing \textit{k} samples from \textit{n} items, where \textit{n} is either a very large or an unknown number \cite{reservoir}. 
In Figure \ref{fig:range_pre_sample}, when $s$ is set to $3$, the result of sampling prediction is much better than linear regression. 
The variance of the normalization between sampling prediction and reduce distribution is because the standard deviation of the prediction results is relatively small compared to the average prediction size, which is $0.0015$ in this example. 
Figure \ref{fig:prediction_relative_error} further proves that the sampling prediction can provide precise result even in the dimension of absolute input size of reduce task. 
On the other hand, the result of linear regression comes out with a large relative error. 
Though the weighted reservoir sampling is precise, it also introduced extra overhead. 
We will show the overhead evaluation of sampling in Section \ref{evaluation}.
% {\color{blue}
% Figure \ref{fig:prediction_relative_error} proves that the sampling prediction can provide much more accurate result than the linear regression. 
% We will show the overhead evaluation of sampling in Section \ref{evaluation}. 
% }

@@

\noindent
\begin{minipage}{0.95\columnwidth}
\begin{algorithm}[H]
\caption{Accumulated Heuristic Scheduling for Multi-Shuffles}
\label{mhminheap}
	\begin{algorithmic}[1]
	\small
	\Procedure{m\_schedule}{$m, host\_id, p\_reduces, \text{\emph{shuffles}}$}
		\State $m\gets$ partition number of map tasks
		\Comment \emph{shuffles} are the previous schedule result 
		\ForAll{$r$ in $p\_reduces$}
			\State $r.size \mathrel{+}= \text{\emph{shuffles}}\left[r.rid\right].size$
			\State $new\_prob\gets \text{\emph{shuffles}}\left[r.rid\right].size / r.size$
			\If{$new\_prob\geq r.prob$}
				\State $r.prob\gets new\_prob$
				\State $r.host\_id\gets \text{\emph{shuffles}}\left[r.rid\right].assigned\_host$
			\EndIf
		\EndFor
		\State $M\gets$ $SCHEDULE\left(m, host\_id, p\_reduces\right)$
		\ForAll{$host\_id$ in $M$}
			\Comment Re-shuffle
			\ForAll{$r$ in $M\left[host\_id\right].reduces$}
				\If{$host\neq \text{\emph{shuffles}}\left[r.rid\right].assigned\_host$}
				\State Re-shuffle data to $host$
				\State $\text{\emph{shuffles}}\left[r.rid\right].assigned\_host\gets host$
				\EndIf
			\EndFor
		\EndFor
		\Return $M$
	\EndProcedure
	\end{algorithmic}
\end{algorithm}
\end{minipage}

>>>>

For the most DAG applications with random large scale input, 
the $BlockSize_{ji}$ in a particular shuffle can be predicted with decent accuracy by liner regression model (i.e., equation \ref{linearregresion}) based on observation that the ratio of map output size and input size are invariant given the same job configuration \cite{guo2017ishuffle, predict}: 
\begin{equation}
\label{linearregresion}
\begin{aligned}
	BlockSize_{ji} = a \times inputSize_j + b
\end{aligned}
\end{equation}
The $inputSize_j$ is the input size of $j$th map task. 
The $a$ and $b$ can be determined using the observed $inputSize_j$ and $BlockSize_{ji}$.

\begin{figure*}
	\centering
	\begin{subfigure}[b]{0.31\linewidth}
		\includegraphics[width=\linewidth]{fig/hash_pre}
		\caption{Linear Regression Prediction of Hash Partitioner\newline}
		\label{fig:hash_pre}
	\end{subfigure}
	\begin{subfigure}[b]{0.31\linewidth}
		\includegraphics[width=\linewidth]{fig/range_pre_sample}
		\caption{Linear Regression and Sampling Prediction of Range Partitioner}
		\label{fig:range_pre_sample}
	\end{subfigure}
	\begin{subfigure}[b]{0.31\linewidth}
		\includegraphics[width=\linewidth]{fig/prediction_relative_error}
		\caption{Prediction Relative Error of Range Partitioner\newline}
		\label{fig:prediction_relative_error}
	\end{subfigure}
	\caption{Reduction Distribution Prediction}
	\label{fig:dis}
	\vspace{-1em}
\end{figure*}

@@

\noindent
\begin{minipage}{0.95\columnwidth}
\begin{algorithm}[H]
\begin{multicols}{2}
\caption{Heuristic MinHeap Scheduling for Single Shuffle}
\label{hminheap}
	\begin{algorithmic}[1]
	\small
	\Procedure{schedule}{$m, host\_ids, p\_reduces$}
		\State $m\gets$ partition number of map tasks
		\State $R\gets$ sort $p\_reduces$ by size in non-increasing order
		\State $M\gets$ min-heap $\left\{ host\_id \rightarrow \left( \left[ reduces \right], size \right) \right\}$
		\State $idx\gets 0$
		\State\While{$idx <$ len$R$}
			% \Comment{Schedule reduces by MinHeap}
			\State $M\left[0\right].size \mathrel{+}= R\left[idx\right].size$
			\State $M\left[0\right].reduces.append\left(R\left[idx\right]\right)$
			\State $R\left[idx\right].assigned\_id \gets M \left[0\right].host\_id$
			\State Sift down $M\left[0\right]$ by $size$
			\State $idx\gets idx-1$
		\EndWhile
		\State $max\gets$ maximum size in $M$
		% \State Convert $M$ to mapping $\left\{ host\_id \rightarrow \left( \left[ rid\_arr \right], size \right) \right\}$
		\ForAll{$reduce$ in $R$}
		\Comment{Heuristic locality swap}
			\If{$reduce.assigned\_id \neq reduce.host\_id$}
				\State $p\gets reduce.prob$
				\State $norm\gets \left(p-1/m\right)/\left(1-1/m\right)/10$
				\State $upper\_bound \gets \left(1 + norm\right) \times max$
				\State SWAP\_TASKS$\left(M, reduce, upper\_bound\right)$
			\EndIf
		\EndFor
		\Return $M$
	\EndProcedure
	\Procedure{swap\_tasks}{$M, reduce, upper\_bound$}
		\State Swap tasks between node $host\_id$ and node $assigned\_id$
		\State of $reduce$ without exceeding the $upper\_bound$
		\State of both nodes.
		\State Return if it is impossible.
	\EndProcedure
	\end{algorithmic}
\end{multicols}
\end{algorithm}
\end{minipage}

To handle this corner case, we introduce another methodology, named \emph{weighted reservoir sampling}, as a substitution of linear regression. 
Note that linear regression will be replaced only when a RangePartitioner or a customized non-hash partitioner occurs. 
For each map task, we use classic reservoir sampling to randomly pick $s \times p$ of samples, where $p$ is the number of reduce tasks and $s$ is a tunable number. 
After that, the map function is called locally to process the sampled data (\textit{Sampling} in Figure \ref{fig:shuffle}). 
Finally, the partitioned outputs are collected with the $InputSize_j$ as the weight of the samples.
Note that sampling does not consume the input data of map tasks. 
The $BlockSize_{ji}$ can be calculated by:
\begin{equation}
\label{equationsample}
\begin{aligned}
	BlockSize_{ji} &= {{InputSize_j \times \frac{sample_i}{s \times p}}} \\
	sample_i &= \text{number of samples for $reduce_i$}
\end{aligned}
\end{equation}
% The classic reservoir sampling is designed for randomly choosing \textit{k} samples from \textit{n} items, where \textit{n} is either a very large or an unknown number \cite{reservoir}. 
% In Figure \ref{fig:range_pre_sample}, when $s$ is set to $3$, the result of sampling prediction is much better than linear regression. 
% The variance of the normalization between sampling prediction and reduce distribution is because the standard deviation of the prediction results is relatively small compared to the average prediction size, which is $0.0015$ in this example. 
% Figure \ref{fig:prediction_relative_error} further proves that the sampling prediction can provide precise result even in the dimension of absolute input size of reduce task. 
% On the other hand, the result of linear regression comes out with a large relative error. 
% Though the weighted reservoir sampling is precise, it also introduced extra overhead. 
% We will show the overhead evaluation of sampling in Section \ref{evaluation}.
{\color{blue}
Figure \ref{fig:prediction_relative_error} proves that the sampling prediction can provide much more accurate result than the linear regression. 
We will show the overhead evaluation of sampling in Section \ref{evaluation}. 
}

@@

\noindent
\begin{minipage}{0.95\columnwidth}
\begin{algorithm}[H]
\caption{Accumulated Heuristic Scheduling for Multi-Shuffles}
\label{mhminheap}
\begin{multicols}{2}
	\begin{algorithmic}[1]
	\small
	\Procedure{m\_schedule}{$m, host\_id, p\_reduces, \text{\emph{shuffles}}$}
		\State $m\gets$ partition number of map tasks
		\Comment \emph{shuffles} are the previous schedule result 
		\ForAll{$r$ in $p\_reduces$}
			\State $r.size \mathrel{+}= \text{\emph{shuffles}}\left[r.rid\right].size$
			\State $new\_prob\gets \text{\emph{shuffles}}\left[r.rid\right].size / r.size$
			\If{$new\_prob\geq r.prob$}
				\State $r.prob\gets new\_prob$
				\State \begin{varwidth}[t]{\linewidth}
					$r.host\_id$ \par
					  \hskip\algorithmicindent $\gets \text{\emph{shuffles}}\left[r.rid\right].assigned\_host$
					\end{varwidth}
			\EndIf
		\EndFor
		\State $M\gets$ $SCHEDULE\left(m, host\_id, p\_reduces\right)$\par
		\hskip\algorithmicindent
		\ForAll{$host\_id$ in $M$}
			\Comment Re-shuffle
			\ForAll{$r$ in $M\left[host\_id\right].reduces$}
				\If{$host\neq$\par
					\hskip\algorithmicindent $\text{\emph{shuffles}}\left[r.rid\right].assigned\_host$}
				\State Re-shuffle data to $host$
				\State $\text{\emph{shuffles}}\left[r.rid\right].assigned\_host$\par
					\hskip\algorithmicindent$\gets host$
				\EndIf
			\EndFor
		\EndFor
		\Return $M$
	\EndProcedure
	\end{algorithmic}
\end{multicols}
\end{algorithm}
\end{minipage}

### 2019-05-24 scache/taco/tex/relatedwork.tex
mkdir scache

{\color{blue}
\textbf{Modeling}: Most representative DAG computing frameworks use similar \textit{Bulk Synchronize Parallel} (BSP)\cite{valiant1990bridging} model to control data synchronization in each computing phase, i.e. \textit{stage} in Spark, \textit{superstep} in Pregel\cite{malewicz2010pregel} and so on. 
% (Hadoop MapReduce can also be considered as a special case of only one superstep in BSP model). 
% In the process of optimizing the shuffle phases between adjacent computing phases, we design a performance model to assist in analyzing computing process.
% There are also lots of performance models for MapReduce have been proposed, such as \cite{verma2011aria, khan2016hadoop, herodotou2011hadoop, chen2014cresp, farhat2016stochastic}.
Verma et al. \cite{verma2011aria} proposed the ARIA model to estimate the required resources based on the job information, the amount of input data and a specified soft deadline.
Khan et al. \cite{khan2016hadoop} proposed the HP model which extends the ARIA model. The HP model adds scaling factors and uses a simple linear regression to estimate the job execution time on larger datasets.
In \cite{herodotou2011hadoop}, Herodotou proposed a detailed set of mathematical performance models for describing the five phases of a MapReduce job abd combine them into an overall MapReduce job model.
% The execution is separated into the phases: Read, Map, Collect, Spill, Merge, Shuffle, Merge, and Reduce. 
% The set of performance models describe each above-mentioned phases and combine into an overall MapReduce job model. 
Chen et al. \cite{chen2014cresp} proposed the CRESP model which is a cost model that estimates the performance of a job then 
provisions the resources for the job.
Farshid Farhat et al.\cite{farhat2016stochastic} proposed a closed-form queuing model which focus on stragglers and try to optimize them. 
% The proposed model is parameterized by the task inter-arrival times to the mappers, the delayed tailed service times, and the number of mappers, which is used to optimize the stragglers. 
However, the above models are not able to accurately describe the overhead caused by the shuffle process under different scheduling strategies. 
% Different from these models, our FRQ model quantifies computing and I/O resources and visualizes them in the time dimension. 
The FRQ model focuses on describing the overhead caused by the shuffle process in different scheduling strategies, which satisfies our demand.
}

>>>>

{\color{blue}
\textbf{Modeling}: Most representative DAG computing frameworks use similar \textit{Bulk Synchronize Parallel} (BSP)\cite{valiant1990bridging} model to control data synchronization in each computing phase, i.e., \textit{stage} in Spark, \textit{superstep} in Pregel\cite{malewicz2010pregel} and so on. 
% (Hadoop MapReduce can also be considered as a special case of only one superstep in BSP model). 
% In the process of optimizing the shuffle phases between adjacent computing phases, we design a performance model to assist in analyzing computing process.
% There are also lots of performance models for MapReduce have been proposed, such as \cite{verma2011aria, khan2016hadoop, herodotou2011hadoop, chen2014cresp, farhat2016stochastic}.
Verma et al. \cite{verma2011aria} proposed the ARIA model to estimate the required resources based on the job information, the amount of input data and a specified soft deadline.
Khan et al. \cite{khan2016hadoop} proposed the HP model which extends the ARIA model. The HP model adds scaling factors and uses a simple linear regression to estimate the job execution time on larger datasets.
In \cite{herodotou2011hadoop}, Herodotou proposed a detailed set of mathematical performance models for describing the five phases of a MapReduce job and combine them into an overall MapReduce job model.
% The execution is separated into the phases: Read, Map, Collect, Spill, Merge, Shuffle, Merge, and Reduce. 
% The set of performance models describe each above-mentioned phases and combine into an overall MapReduce job model. 
Chen et al. \cite{chen2014cresp} proposed the CRESP model which is a cost model that estimates the performance of a job then 
provisions the resources for the job.
Farshid Farhat et al.\cite{farhat2016stochastic} proposed a closed-form queuing model which focus on stragglers and try to optimize them. 
% The proposed model is parameterized by the task inter-arrival times to the mappers, the delayed tailed service times, and the number of mappers, which is used to optimize the stragglers. 
However, the above models are not able to accurately describe the overhead caused by the shuffle process under different scheduling strategies. 
% Different from these models, our FRQ model quantifies computing and I/O resources and visualizes them in the time dimension. 
The FRQ model focuses on describing the overhead caused by the shuffle process in different scheduling strategies, which satisfies our demand.
}

### 2019-05-24 scache/tii/tex/abstract.tex
mkdir scache

% In large-scale data-parallel analytics, shuffle, or the cross-network read and aggregation of partitioned data between tasks with data dependencies, usually brings in large overhead. 
% {\color{black}
In industrial large-scale data-parallel analytics, shuffle, or the cross-network read and the aggregation of partitioned data between tasks with data dependencies, usually bring in large overhead.
Due to the dependency constraints, execution of those descendant tasks could be delayed by long shuffles.
To reduce shuffle overhead, we present \textit{SCache}, an open source plug-in system that particularly focuses on shuffle optimization. 
SCache adopt heuristic pre-scheduling combining with shuffle size prediction to pre-fetch shuffle data and balance load on each node. 
% By extracting and analyzing shuffle dependencies prior to the actual task execution, SCache can adopt heuristic pre-scheduling combining with shuffle size prediction to pre-fetch shuffle data and balance load on each node. 
Meanwhile, SCache takes full advantage of the system memory to accelerate the shuffle process. 
% {\color{red}
% We have implemented SCache and customized Spark to use it as the external shuffle service and co-scheduler. The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster.
% Those evaluations have demonstrated that, by incorporating SCache, the shuffle overhead of Spark can be reduced by nearly $89\%$, and the overall completion time of TPC-DS queries improves $40\%$ on average.
% }
{\color{black}
We also propose a new performance model called \textit{Framework Resources Quantification} (FRQ) model to analyze DAG frameworks and evaluate the SCache shuffle optimization. 
The FRQ model quantifies the utilization of resources and predicts the execution time of each phase of computing jobs. 
% We use the FRQ model to analyze DAG frameworks and evaluate the SCache shuffle optimization by mathematics.
We have implemented SCache on both Spark and Hadoop MapReduce. The performance of SCache has been evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster.
Those evaluations have demonstrated that, by incorporating SCache, the shuffle overhead of Spark can be reduced by nearly $89\%$, and the overall completion time of TPC-DS queries improves $40\%$ on average. On Apache Hadoop MapReduce, SCache optimizes end-to-end Terasort completion time by $15\%$.
}
\end{abstract}

>>>>

% In large-scale data-parallel analytics, shuffle, or the cross-network read and aggregation of partitioned data between tasks with data dependencies, usually brings in large overhead. 
% {\color{blue}
In industrial large-scale data-parallel analytics, shuffle, or the cross-network read and the aggregation of partitioned data between tasks with data dependencies, usually bring in large overhead.
Due to the dependency constraints, execution of those descendant tasks could be delayed by long shuffles.
To reduce shuffle overhead, we present \textit{SCache}, an open source plug-in system that particularly focuses on shuffle optimization. 
By extracting and analyzing shuffle dependencies prior to the actual task execution, SCache can adopt heuristic pre-scheduling combining with shuffle size prediction to pre-fetch shuffle data and balance load on each node. 
Meanwhile, SCache takes full advantage of the system memory to accelerate the shuffle process. 
% {\color{red}
% We have implemented SCache and customized Spark to use it as the external shuffle service and co-scheduler. The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster.
% Those evaluations have demonstrated that, by incorporating SCache, the shuffle overhead of Spark can be reduced by nearly $89\%$, and the overall completion time of TPC-DS queries improves $40\%$ on average.
% }
{\color{blue}
We also propose a new performance model called \textit{Framework Resources Quantification} (FRQ) model to analyze DAG frameworks and evaluate the SCache shuffle optimization. 
The FRQ model quantifies the utilization of resources and predicts the execution time of each phase of computing jobs. 
% We use the FRQ model to analyze DAG frameworks and evaluate the SCache shuffle optimization by mathematics.
We have implemented SCache on both Apache Spark and Apache Hadoop MapReduce. The performance of SCache has been evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster.
Those evaluations have demonstrated that, by incorporating SCache, the shuffle overhead of Spark can be reduced by nearly $89\%$, and the overall completion time of TPC-DS queries improves $40\%$ on average. On Apache Hadoop MapReduce, SCache optimizes end-to-end Terasort completion time by $15\%$.
}
\end{abstract}

### 2019-05-24 scache/tii/tex/evaluation.tex
mkdir scache

\section{Evaluation}\label{evaluation}
This section reveals the evaluation of SCache with comprehensive workloads and benchmarks. 
First we run a job with single shuffle to analyze hardware utilization and see the impacts of different components from the scope of a task to a job. 
Then we use a recognized shuffle intensive benchmark --- Terasort to evaluate SCache with different data partition schemes.

% \begin{figure}
% 	\includegraphics[width=.8\linewidth]{fig/scache_util}
% 	\caption{CPU utilization and I/O throughput of a node during a Spark single shuffle application with SCache}
% 	\label{fig:scache_util}
% \end{figure}

In order to prove the performance gain of SCache with a real production workload, we also evaluate Spark TPC-DS\footnote{https://github.com/databricks/spark-sql-perf} and present the overall performance improvement.
{\color{blue}
To prove the compatibility of SCache as a cross-framework plug-in, we implemented SCache on both Hadoop MapReduce and Spark. 
Due to the simple DAG computing in Hadoop MapReduce, we only use Terasort as a shuffle-heavy benchmark to evaluate the performance of Hadoop MapReduce with SCache.
}
Finally, we measure the overhead of weighted reservoir sampling. 
In summary, SCache can decrease ~$89\%$ time of Spark shuffle without introducing extra network transfer.
More impressively, the overall completion time of TPC-DS can be improved ~$40\%$ on average by applying the optimization from SCache.
{\color{blue}Meanwhile, Hadoop MapReduce with SCache optimizes job completion time by up to $15\%$ and an average of $13\%$}

@@

In overall, SCache can help Spark decrease by ~$89\%$ overhead of the whole shuffle process.

\subsection{Terasort}
We also evaluate Terasort-a recognized shuffle intensive benchmark for distributed system analysis. 
Terasort consists of two consecutive shuffles. 
The first shuffle reads the input data and uses a hash partition function for re-partitioning. 
As shown in Figure \ref{fig:terasort}, Spark with SCache runs 2 $\times$ faster during the reduce stage of the first shuffle, which is consistent with the results in Section \ref{simpledag}. 
It further proves the effectiveness of SCache's optimization.

The second shuffle of Terasort partitions the data through a Spark RangePartitioner. 
% As the range bounds set by range partitioner almost match the same pattern of the first shuffle, almost $93\%$ of input data is from one particular map task for each reduce task. So we take the second shuffle as an extreme case to evaluate the scheduling locality for SCache.
In the second shuffle, almost $93\%$ of input data of a reduce task is produced by one particular map task. 
So we take the second shuffle as an extreme case to evaluate the heuristic locality swap of SCache.
In this shuffle, Spark schedules a reduce task to the node that produces most input data. 
By doing this, Spark minimizes the shuffle data through network. 
At the same time, Figure \ref{fig:terashuffle} reveals that SCache produces exactly same network traffic as Spark. 
It implies that the heuristic locality swap of SCache can obtain the best locality while balancing the load. 
\begin{figure*}
	\centering
	\begin{subfigure}{.47\linewidth}
		\includegraphics[width=\linewidth]{fig/hadoop_terasort_scache}
		\caption{\color{blue}Hadoop MapReduce with SCache}
		\label{fig:hadoop_terasort_scache}
	\end{subfigure}
	\begin{subfigure}{.47\linewidth}
		\includegraphics[width=\linewidth]{fig/hadoop_terasort_origin}
		\caption{\color{blue}Hadoop MapReduce without SCache}
		\label{fig:hadoop_terasort_origin}
	\end{subfigure}
	\caption{\color{blue}CPU utilization and I/O throughput of a node during a Hadoop MapReduce Terasort job}
	\label{fig:hadoop_terasort}
\end{figure*}
\begin{figure*}
	\centering
	\includegraphics[width=.9\textwidth]{fig/tpcds}
	\caption{TPC-DS Benchmark Evaluation}
	\label{fig:tpcds}
	\vspace{-1em}
\end{figure*}

>>>>

\section{Evaluation}\label{evaluation}
{\color{blue}
This section reveals the evaluation of SCache with comprehensive workloads and benchmarks which include common operations in the industrial big-data analysis. 
% To show the compatibility of SCache as a cross-framework plug-in, we implement and evaluate SCache on both Spark and Hadoop MapReduce. 
We implement and evaluate SCache on Spark and Hadoop MapReduce, since they are the two most distributed computing frameworks using in industrial big-data analysis.
First, we evaluate the Spark with SCache in 3 different benchmarks.
We run a Spark job with single shuffle to analyze hardware utilization and see the impacts of different components from the scope of a task to a job. 
Then we use a recognized shuffle intensive benchmark --- Terasort to evaluate SCache with different data partition schemes.
To prove the performance gain of SCache with a industrial production workload, we also evaluate Spark TPC-DS\footnote{https://github.com/databricks/spark-sql-perf} and present the overall performance improvement.
% In order to prove the performance gain of SCache with a real production workload, we also evaluate Spark TPC-DS\footnote{https://github.com/databricks/spark-sql-perf} and present the overall performance improvement.
% To prove the compatibility of SCache as a cross-framework plug-in, we implemented SCache on both Hadoop MapReduce and Spark. 
Second, due to the simple DAG computing in Hadoop MapReduce, we only use Terasort as a shuffle-heavy benchmark to evaluate the performance of Hadoop MapReduce with SCache.
}
Finally, we measure the overhead of weighted reservoir sampling.

In summary, SCache can decrease ~$89\%$ time of Spark shuffle without introducing extra network transfer.
More impressively, the overall completion time of TPC-DS can be improved ~$40\%$ on average by applying the optimization from SCache.
{\color{blue}Meanwhile, Hadoop MapReduce with SCache optimizes job completion time by up to $15\%$ and an average of $13\%$}

@@

Overall, SCache can help Spark decrease by ~$89\%$ overhead of the whole shuffle process.

\subsubsection{Terasort}
We also evaluate Terasort\cite{terasort} --- a recognized shuffle intensive benchmark for distributed system analysis. 
Terasort consists of two consecutive shuffles. 
The first shuffle reads the input data and uses a hash partition function for re-partitioning. 
As shown in Figure \ref{fig:terasort}, Spark with SCache runs 2 $\times$ faster during the reduce stage of the first shuffle, which is consistent with the results in Section \ref{simpledag}. 
It further proves the effectiveness of SCache's optimization.

The second shuffle of Terasort partitions the data through a Spark RangePartitioner. 
% As the range bounds set by range partitioner almost match the same pattern of the first shuffle, almost $93\%$ of input data is from one particular map task for each reduce task. So we take the second shuffle as an extreme case to evaluate the scheduling locality for SCache.
In the second shuffle, almost $93\%$ of input data of a reduce task is produced by one particular map task. 
So we take the second shuffle as an extreme case to evaluate the heuristic locality swap of SCache.
In this shuffle, Spark schedules a reduce task to the node that produces most input data. 
By doing this, Spark minimizes the shuffle data through network. 
At the same time, Figure \ref{fig:terashuffle} reveals that SCache produces exactly same network traffic as Spark. 
It implies that the heuristic locality swap of SCache can obtain the best locality while balancing the load. 
\begin{figure*}
	\centering
	\includegraphics[width=.9\textwidth]{fig/tpcds}
	\caption{TPC-DS Benchmark Evaluation}
	\label{fig:tpcds}
	\vspace{-1em}
\end{figure*}

\subsubsection{Industrial Production Workload}
We also evaluate some queries from TPC-DS\footnote{http://www.tpc.org/tpcds/}. 
TPC-DS benchmark is designed for modeling multiple users submitting varied queries (e.g. ad-hoc, interactive OLAP, data mining, etc.). 
TPC-DS contains 99 queries and is considered as the standardized industry benchmark for testing big data systems. 
% We evaluate the performance of Spark with SCache by picking some of the TPC-DS queries with shuffle intensive attribute. 
As shown in Figure \ref{fig:tpcds}, the horizontal axis is query name and the vertical axis is query completion time. 
Note that we skip some queries due to the compatible issues. 
Spark with SCache outperforms the original Spark in almost all tested queries. 
Furthermore, in many queries, Spark with SCache outperforms original Spark by an order of magnitude. 
It is because that those queries contain shuffle-heavy operations such as \textit{groupby}, \textit{union}, etc.
The overall reduction portion of query time that SCache achieved is $40\%$ on average. 
Since this evaluation presents the overall job completion time of queries, we believe that our shuffle optimization is promising.

\begin{figure*}
	\centering
	\begin{subfigure}{.47\linewidth}
		\includegraphics[width=\linewidth]{fig/hadoop_terasort_scache}
		\caption{\color{blue}Hadoop MapReduce with SCache}
		\label{fig:hadoop_terasort_scache}
	\end{subfigure}
	\begin{subfigure}{.47\linewidth}
		\includegraphics[width=\linewidth]{fig/hadoop_terasort_origin}
		\caption{\color{blue}Hadoop MapReduce without SCache}
		\label{fig:hadoop_terasort_origin}
	\end{subfigure}
	\caption{\color{blue}CPU utilization and I/O throughput of a node during a Hadoop MapReduce Terasort job}
	\label{fig:hadoop_terasort}
\end{figure*}
